\documentclass[12pt]{article}

% Import essential packages from imports.tex
\input{sections/imports}

\begin{document}

% Title page
\input{sections/title}

\tableofcontents
\newpage

% Abstract Section
\input{sections/abstract.tex}

% Problem Description and Specification
\input{sections/problem-description.tex}

% Design and Solution
\input{sections/design.tex}

\newpage

% Testing and Results
\section{Testing and Results}
\subsection{Testing Procedure}
\begin{enumerate}[leftmargin=2em]
    \item Initialize the system and ensure peripheral communication.
    \item Measure and compute frequency and resistance.
    \item Validate ADC and DAC outputs in real-time.
    \item Toggle modes and observe transitions.
\end{enumerate}

\subsection{Results}
\begin{itemize}[leftmargin=2em]
    \item \textbf{Frequency Calculation Accuracy:} Deviation $<$ 2\%.
    \item \textbf{Resistance Calculation Accuracy:} Robust under varying loads.
    \item \textbf{Noise Mitigation:} Effective filtering techniques implemented.
\end{itemize}

% Discussion and Conclusion
\section{Discussion and Conclusion}
\subsection{Challenges}
\begin{itemize}[leftmargin=2em]
    \item Signal noise required advanced filtering strategies.
    \item Interrupt handling presented synchronization issues.
\end{itemize}

\subsection{Future Work}
\begin{itemize}[leftmargin=2em]
    \item Increase sampling rates for improved resolution.
    \item Integrate advanced noise reduction algorithms.
\end{itemize}

\subsection{Conclusion}
The project demonstrates a reliable, modular design for real-time signal processing, providing a strong foundation for further enhancements.

% References
\section{References}
\printbibliography[title={}]
\end{document}	